Blocking-resistant communication through high-value web services

### 2014-05-12 docs/meek.tex
Rename paper.tex → meek.tex.
Title.

@@

\cite{ccs2012-decoys}
% Routing around decoys
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is still questionable whether ISPs are
willing to act against state-level censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.

@@

\bibliographystyle{plain}  
\bibliography{paper}

>>>>

\title{Blocking-resistant communication through high-value web services}
\author{David Fifield, Chang Lan}

@@

\cite{ccs2012-decoys}
% Routing around decoys
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is not clear whether ISPs are
willing to act against censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.

@@

\bibliographystyle{plain}  
\bibliography{meek}
